GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-23 paper/paper.tex
new pdf

\section{Related Work}
Traditionally, recommender systems are classified into the following three categories: 
1. User-based Collaborative Filtering Systems~\cite{Herlocker}:
The user will be recommended items similar to the ones the user preferred in the past.
2. Item-based Collaborative Filtering Systems~\cite{Sarwar, Linden}:
The user will be recommended items that people with similar tastes and preferences liked in the past.
3. Hybrid Recommender Systems[Reference 2篇]:
These methods combine the above two methods.
They usually suggest books, music albums, from a set of input parameters, possibly including user profiles, purchase history, etc.

In recent years, many researchers use novel technology to recommend, e.g. Edward use Commonsense to recommend clothing [ ].   Furthermore, some researchers use recommender system in interesting domains, such as Cosley’s Movie Recommendation[ ], and Koutrika’s Course Recommendation[ ].   Moreover, the display style of Top 10 is popular again recently []. We follow the latest trend, and use the novel technology in interesting domain.   In short, we are the first one that combine traditional recommendations and Commonsense, and apply them in Gift Recommendation.

@@

\subsection{Flow}
Users of our recommender system start with filling in their considerations on the UI interface. (For reducing the loading of senders, we use check box and combo box and make a lot of common options.)   
After filling in the options and considerations, the users will be greeted  a list of 20 recommended gifts generated by the system from the information provided by the users.
If the users want more information on the recommended gift item, they can click the link and the system will help the users to find the relative products from several popular e-commerce websites.

@@

\subsection{UI Design}
The UI of the GiftGiver is given in Figure~\ref{ui}, it is a website with a rich set of options for users to choose his/her preference for the gifts. We categorize the questions in to 3 main parts, the main considerations, the Receiver profile and the Result based on the result of the questionnaire. Originally we considered both the features and preference of the sender and the receiver, however we want to learn more about what might be the influencial factors for picking gifts.  We designed a questionnaire to ask 3 adult females and 10 adult males about what they will consider when they sent a gift.
(The question is like “when you are picking a gift, is the relation between you and receiver seems important to you?”)   Each question has a scale from 1 to 5, from unimportant to most important.

(From the result table, we can separate the score in to 3 part – Red (score> 4), pink (4>score>3), and green (3>score).  The red part is the most important union.  Such as relationship, price, sender’s gender etc. This result is quiet reasonable.   In general, the gift will finally own by the receiver than own by both sender and receiver.   So the options about receivers are higher than the options about senders.  In other part, price, occasion, sent date and receiver’s gender are common to affect whether the gift is reasonable.)

Furthermore, we interviewed 5 differnet people with the primary concerns when picking a nice gift. We later found out the result of the interviews that they agreeed the same considerations with the questionnaire results. The results had shown that people  concern about the occasion more than relationship.  Other considerations did not seem to influence too much to the decision making process compared to occasion and relationship.

@@

Compare to major e-commerce websites that sells real products, our website doesn't have the real database for all different kinds of gifts, but we had a better flow and more variety and flexibility of options for users to pick. There is also another extinction between our UI design and those of major corporations. For example, Gifts.com has 9 ages degree, such as [0-6], [7-12], [13-19], [20-30], [31-40] etc, we use fuzzy set to define our age instead of clear separation by years. Because nouns like child, adult etc. will help the system in the commonsense part.  On the other hand, some people still looks like a child even that person has already more than 30s.  The fuzzy part will come out positive result.

>>>>

\section{Related Work}
Traditionally, recommender systems are classified into the following three categories: 
1. User-based Collaborative Filtering Systems~\cite{Herlocker}:
The user will be recommended items similar to the ones the user preferred in the past.
2. Item-based Collaborative Filtering Systems~\cite{Sarwar, Linden}:
The user will be recommended items that people with similar tastes and preferences liked in the past.
3. Hybrid Recommender Systems~\cite{Bruke}:
These systems combined the above two systems.
They usually suggest books, music albums, from a set of input parameters, possibly including user profiles, purchase history, etc.

In recent years, many researchers use novel technology to recommend, e.g. Edward use Commonsense to recommend clothing~\cite{Shen}.   Furthermore, some researchers use recommender system in interesting domains, such as Cosley’s Movie Recommendation~\cite{Cosley}, and Koutrika’s Course Recommendation~\cite{Koutrika}.   Moreover, the display style of Top 10 is popular again recently~\cite{Deutch}. We follow the latest trend, and use the novel technology in interesting domain.   In short, we are the first one that combine traditional recommendations and Commonsense, and apply them in Gift Recommendation.

@@

\subsection{Flow}
Users of our recommender system start with filling in their considerations on the UI interface.

After filling in the options and considerations, the users will be greeted  a list of 20 recommended gifts generated by the system from the information provided by the users.
If the users want more information on the recommended gift item, they can click the link and the system will help the users to find the relative products from several popular e-commerce websites.

@@

\subsection{UI Design}
The UI of the GiftGiver is given in Figure~\ref{ui}, it is a website with a rich set of options for users to choose his/her preference for the gifts. We categorize the questions in to 3 main parts, the main considerations, the Receiver profile and the Result based on the result of the questionnaire. Originally we considered both the features and preference of the sender and the receiver, however we want to learn more about what might be the influencial factors for picking gifts.  We designed a questionnaire to ask 3 adult females and 10 adult males about what they will consider when they sent a gift. Each question has a scale from 1 to 5, from unimportant to most important.

Furthermore, we interviewed 5 differnet people with the primary concerns when picking a nice gift. We later found out the result of the interviews that they agreeed the same considerations with the questionnaire results. The results had shown that people  concern about the relationship more than occasion.  Other considerations did not seem to influence too much to the decision making process compared to occasion and relationship.

@@

Compare to major e-commerce websites that sells real products, our website doesn't have the real database for all different kinds of gifts, but we had a better flow and more variety and flexibility of options for users to pick. There is also another extinction between our UI design and those of major corporations. For example, Gifts.com has more than 10 ages degree, such as $0~6$, $7~12$, $13~19$, $20~30$, $31~40$ etc, we use fuzzy set to define our age instead of clear separation by years. Because nouns like child, adult etc. will help the system in the commonsense part.  On the other hand, some people still looks like a child even that person has already more than 30s.  The fuzzy part will come out positive result.
